Pangenome graph layout by Path-Guided Stochastic Gradient Descent

### 2023-07-28 manuscript/main.tex
feedback jiajie

	\FIXME{@Jiajie + Niklas: Maybe address our SMT issue with your cache locality as a potential solution. Additionally just 2/3 sentences about going GPU?}

>>>>

	\FIXME{@Jiajie + Niklas: Maybe address our SMT issue with your cache locality as a potential solution. Additionally just 2/3 sentences about going GPU?}
	As can especially be observed in the chromosome 16 evaluation results, the implementation is memory-bound. The current data structure doesn't consider the memory access pattern. Therefore, a CPU cache optimized implementation can make use of the massive parallelized calculations on a GPU.
